%
% Example based on documentation for the songs project:
% http://songs.sourceforge.net/
%
\documentclass{article}
\usepackage[chorded]{songs}

\noversenumbers

\begin{document}
\songsection{Worship Songs}

\begin{songs}{}

\beginsong{}
\beginverse
 Capo 2
\endverse
\beginverse
\[C]To the church of \[F]God which is \[G]in Cor\[C]inth,
To those who h\[F]ave
Been sanctif\[G]ied in Christ J\[C]esu\[C7]s,
The called s\[F]aints, with all th\[G]ose
Who call upon the \[Em]name of our Lord Jesus Ch\[Am]rist
In every p\[F]lace,
Who is theirs and \[G]ours
\endverse
\beginverse
Who call upon the \[C]name of our Lord Jesus \[F]Christ
In every \[Am]place\[G]
Who call upon the \[C]name of our Lord Jesus \[F]Christ
In every \[Am]place\[G]
Who is theirs and \[C]ours.
\endverse
\beginverse

 1 Corinthians 1:2
\endverse
\endsong{}
\beginsong{}
\beginverse
 Capo 1
\endverse
\beginverse
1
\[D]Don’t you want to \[Bm]know your God?
What’s \[Fm]hidden in His \[G]heart for you?
How \[D]much He longs for \[G]you to come
And \[Em7]open \[A]up—
To \[D]let Him in to \[A]every part,
Let \[F7]Him reveal what’s \[Bm]on His heart;
What \[G]was the joy \[A]set before \[Bm]Him? \[D7]
\endverse
\beginverse
  It \[Bm]was for her, the \[D]church—His Bride,
  It \[G]was for her, willing\[Bm]ly He died.
  She \[G]is the joy deep \[A]in His heart.
  His \[Bm]masterpiec\[G]e—
  His \[A]counter\[D]part.
\endverse
\beginverse
2
The Lord chose you to be a part
Of His great plan, His work of art.
What wonder! What a privilege
To satisfy
His yearning to share all He is—
Divine, unsearchable riches!
What wisdom, multifarious expressed?
\endverse
\beginverse
3
As we enjoy and enter in
To all He is then we’ll begin
To understand the feeling in
His heart toward us.
What love that motivated Him!
To come to us, despite our sin.
Why did He go and sell all that He had?
\endverse
\endsong{}
\beginsong{}
\beginverse
1
Splendid \[G]church life! His green garden!
He has \[C]brought us, praise the Lord,
To ex\[D]perience the Christ
Who's growing \[G]here!
He is \[]full of rich enjoyment
To His \[C]saints in one accord;
He is \[D]new and fresh, a\[D7]vailable and \[G-C-G]dear.
\endverse
\beginverse
  I'm so \[G7]happy \[C]in this lovely place,
  \[D]In the garden \[D7]growing in His \[G]grace!
  \[]There is no finer pleasure
  Than to \[C]eat the living tree
  And to \[D]get the living \[D7]water into \[G-C-G]me.
\endverse
\beginverse
2
It is not a school or fact'ry
Or a chapel in the air;
But a garden where our Lord
Can plant and sow.
So He's placed us all here corporately
To be His garden fair,
Where He's free to cultivate
And make us grow.
\endverse
\beginverse
3
Thus within the church-life garden
There's a fruit-producing tree
Full of life and so available to eat.
So be simple, don't be hardened,
Drop your concepts—eat that tree!
Take in Jesus every moment—He's so sweet!
\endverse
\beginverse
4
With the tree there is the water,
Flowing God in Christ to us,
Quenching all our dryness,
Ending all our strife.
Hallelujah! In His garden
Jesus flows Himself to us,
As the full supply for us to grow in life.
\endverse
\beginverse
5
Aren't you satisfied and thankful
That our Lord has brought you in
Where His pleasures and His riches
Flow so free?
So be happy and be joyful,
In the spirit feast on Him,
So God's garden can bear fruit abundantly.
\endverse
\endsong{}
\beginsong{}
\beginverse
 Capo 2
\endverse
\beginverse
\[C]I’m so \[CM7]happy here,
\[Dm]With my \[Dm7]Father dear,
\[G]Once lost, \[G7]now I’m near a\[C]gain\[CM7]!
(It was) \[C]First His \[CM7]smiling face,
\[Dm]Then His \[Dm7]warm embrace,
\[G]I’m surp\[G7]rised by grace a\[C]gain!\[C7]
\endverse
\beginverse
  I was \[F]lost, now I’m \[Em]found again!
  I was \[F]dead, but \[Dm7]now I \[G]live!
  Come rej\[F]oice with us, and be \[Em]merry then.
  \[Dm]Back in my \[G7]Father’s house a\[C]gain!\[CM7]
\endverse
\beginverse
Robe, ring, sandals on
And my hunger’s gone!
Back where I belong, again!
(Because He) Clothed me thoroughly,
(And then He) Reinstated me!
(Now I’m) Back in the family again!
\endverse
\endsong{}
\beginsong{}
\beginverse
 Adapted from 2014 Spring ITERO, Message 7
Capo 3
\endverse
\beginverse
\[G]Jacob saw the vision of a dream in Bethel,
\[D]Moses saw the vision on a m\[C]ountain, \[Cm]do tell,
\[G]David saw the vision of the \[E7]holy temple,
E\[A]zekiel saw the \[D]vision of the \[G]house.
 
  Then \[G]John.... saw the vision of the \[C]New Je\[D]rusa\[G]lem,
  Well, it’s God\[E7].... dispensed and \[A]God built into \[D]men,
  \[G]We need a vision so we \[G7]open to the Lord,
  \[C]Seeking revelation in the H\[A7]oly Word,
  \[G]Turning to the spirit for the \[E7]building of the church,
  The \[A]church is the \[D7]fullness of the \[G]One.
  (Ep\[A]hesians \[D7]one: twenty th\[G]ree)
\endverse
\beginverse
Zechariah’s vision was for God’s recovery,
Daniel had a vision of Christ in victory,
Paul and Peter’s vision of the building of the Body
Complete the revelation of the age.
\endverse
\endsong{}
\beginsong{}
\beginverse
1
Oh, the \[G]church of Christ is \[G7]glorious,
And \[C]we are part of \[G]it—
\[]We're so happy that
The \[Em]Lord has made us \[D]one\[D7]!
There's a \[G]Body in the \[G7]universe
And \[C]we belong to \[G]it—
Hallelujah, for the \[D]Lord has made us \[G]one!
\endverse
\beginverse

  Hallelujah for the Body!
  We are \[Am]members of the \[D]Body!
  We are \[G]wholly for the \[C]Bo\[Am]dy!
  Halle\[G]lujah, for the \[D]Lord has made us \[G]one!
\endverse
\beginverse
2
Not the individual Christians,
But a corporate entity—
God must have it for His full expression now;
Not just individual churches but the
Body corporately—
Hallelujah, we are in the Body now!
\endverse
\beginverse
  Hallelujah for the Body!
  Satan trembles at the Body!
  We're victorious in the Body!
  Hallelujah, we are in the Body now!
\endverse
\beginverse
3
There are seven golden lampstands in the
nature all divine—
Nothing natural does the Body life allow.
When we're one and share God's nature,
How the lampstand then does shine—
Hallelujah, it is brightly shining now!
\endverse
\beginverse
  Hallelujah for the Body!
  For the lampstands of the Body!
  For the golden, shining Body!
  Hallelujah, it is brightly shining now!
\endverse
\beginverse
4
How may we express such oneness,
Be divine and shining too?
Hallelujah, eating Jesus is the way!
He's the tree of life, the manna,
And the feast that's ever new—
Hallelujah, we may eat Him every day!
\endverse
\beginverse
  We are one by eating Jesus!
  We're divine by eating Jesus!
  How we shine by eating Jesus!
  Hallelujah, eating Jesus is the way!
\endverse
\endsong{}
\beginsong{}
\beginverse
Capo 3
1
Re\[D]call how David s\[Fm]wore,
"I'll \[G]not come into \[A]my house,\[A7]
Nor \[D]go up to my \[Fm]bed,
Give \[G]slumber to mine \[A]eyelids,\[A7]
Un\[G]til I find a \[D]place for Thee,
\[Em]A pl\[A]ace, O L\[Fm]ord, for T\[Bm]hee."
Our \[G]mighty \[D]God de\[G]sires a \[D]home
Where \[G]all His \[A]own may \[D]come.
\endverse
\beginverse
2
How blinded we have been,
Shut in with what concerns us;
While God's house lieth waste—
Lord, break through, overturn us;
We'll go up to the mountain,
Bring wood and build the house;
We'll never say, "Another day!"
It's time! We'll come and build!
\endverse
\beginverse
3
O Lord, against these days,
Inspire some for Your building,
Just as in David's day—
A remnant who are willing
To come and work in Your house,
Oh, what a blessed charge!
Your heart's desire, is our desire—
We come, O Lord, to build.
\endverse
\beginverse
4
Within those whom You'd call
Put such a restless caring
For building to give all—
These times are for preparing;
The gates of hell cannot prevail
Against the builded Church!
The hours are few, the builders too—
Lord, build, O build in us!
\endverse
\beginverse
(Repeat the last four lines)
\endverse
\endsong{}
\beginsong{}
\beginverse
1
\[C]Never \[G]did I dream be\[C-F]fore,
Such a \[G]place could e'er be \[C]found,
Where the \[G]tears of sorrow \[C-F]cease,
Songs of \[G]endless joy \[C]abound.
One who \[F]seldom ever \[Em-Am]sang,
\[Dm]Now delights his voice to \[G-G7]raise;
Singing \[F]hymns with all the \[Em-Am]saints,
\[Dm]Echo\[G]ing the ceaseless \[C]praise.
\endverse
\beginverse
2
Day by day the world goes on,
Just as it has gone before.
Millions grasp and clutch at life,
Wond'ring if there could be more;
Such was I and would be, yet
Mercy found me out somehow;
With what gratefulness I say,
"I'm in God's own family now."
\endverse
\beginverse
3
How delightful 'tis to know;
How subjective, real, and sweet
Is this inward joy of grace
We experience when we meet;
Life abundant Jesus gives
As my full reality;
Praise You, Lord, it's really true,
I'm in Your own family.
\endverse
\beginverse
4
At the closing of this age,
Just before Your kingdom's dawn,
May You gain a people, Lord,
For Your dwelling place, Your home.
Since for me You gave Your all,
Everything I lay aside;
For Your church my all I'd give,
That You would be satisfied.
\endverse
\endsong{}
\beginsong{}
\beginverse
1
\[D]The church is t\[A]he building up\[Bm]
Of all God's \[Fm]chosen and re\[G]deemed,
Regene\[D]rated and trans\[G]formed peop\[A]le.
\[D]The ultimate work of God\[A],
His counterpart, the new ma\[Bm]n,
The seven golden lamp\[Fm]stands,
God's house on \[G]earth,
The Body of \[D]Christ,
The de\[G]sire \[A]of God's \[D]heart.
\endverse
\beginverse
2
Praise the Lord\[A]! Philad\[Bm]elphia\[Fm].
They \[G]hold fast to \[D]God's Word,
\[Em]Never denying His \[A]name,
\[D]Living \[A]in the local \[Bm]church
\[Fm]Fellowshipping universal\[G]ly,
On the \[D]ground of genuine \[G]oneness,
Constit\[A]uting the Body of \[D]Christ.
\endverse
\beginverse
3
Rise up!\[A] Grow in l\[Bm]ife!
\[Fm]Minister Christ to the \[G]nations,
Ar\[D]rive at \[Em]oneness \[A]— Lord have \[D]mercy,
We would see\[A] Your eternal p\[Bm]urpose\[Fm],
Keep us \[G]faithful
To re\[D]cover and \[G]build \[A]up Your \[D]church.
\endverse
\endsong{}


\end{songs}


\end{document}